A Guide to Pre-Processing High-Throughput Animal Tracking Data

### 2021-02-04 docs/ms_atlas_preproc_main_text.tex
add main text tex

\begin{figure}
    \centering
    \includegraphics[width=0.99\textwidth]{figures/fig_01_recipe.png}
    \caption{A general, modular pipeline for pre-processing high-throughput tracking data from raw localisations to cleaned data, and optionally into residence patches. 
    Users should begin by plotting their data to determine its status, for instance whether it needs to be susbet within a certain time interval, or whether there are obvious location errors.
    Users can then pre-process their data using the appropriate module, following the pre-processing steps corresponding to each module.
    The \texttt{atlastools} function that may be used to implement each pre-processing step is shown in the grey boxes underneath each step.
    Users may use the pipeline in full or just the module most appropriate for their data.
    In all cases, users are strongly encouraged to visualise their data and scan it for location errors as a first step, and to visualise it along the way.
    }
    \label{fig:figure_pipeline}
\end{figure}

@@

    \item After data access, we first encourage users to visualise their data to check for evident location errors \citep{slingsby2016}.
    \item Users can install \texttt{atlastools} using the \texttt{install\_github} function from the \texttt{R} package \texttt{remotes}.
    The package can be installed using the \texttt{R} command

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.99\textwidth]{figures/fig_01_recipe.png}
    \caption{A general, modular pipeline for pre-processing high-throughput tracking data from raw localisations to cleaned data, and optionally into residence patches. 
    Users should determine the appropriate pre-processing module, and work their way through the corresponding pre-processing steps, until the data are suitable for their intended purpose.
    The \texttt{atlastools} function that may be used to implement each pre-processing step is shown in the grey boxes underneath each step.
    Popular \texttt{R} packages in movement ecology, or statistical methods are shown underneath suggested analyses (yellow boxes).
    Users are strongly encouraged to visualise their data and scan it for location errors as a first step, and as they work through the pipeline.
    }
    \label{fig:figure_pipeline}
\end{figure}

@@

    \item Users should visualise their data to check for evident location errors \citep{slingsby2016}.
    \item Users can install \texttt{atlastools} using the \texttt{install\_github} function from the \texttt{R} package \texttt{remotes}.
    The package can be installed using the \texttt{R} command
